Writing Trash Bin

### 2024-02-27 writingdumpster.qmd
word vomit of great ideas and updated edit notes

@@

- Heuristics can work against us just as much as they can work for us. The sine illusion can cause the confidence interval of a smoothed sine curve to seem wider at the peaks than the troughs, causing us to underestimate uncertainty associated with changing values [@Vanderplas2015]
- mentions uncertainty can be variance, precision, accuracy, reliability, or related concepts @Hullman2016
-  @Spiegelhalter2017 defines risk as risk known probabilities and uncertainty as estimated probabilities, therefore uncertainty is what we have when you cannot accurately quantify risk.
- Authors provide little justification for their chosen response models (e.g. absolute accuracy vs relative measures) @Hullman2016 
- Some questions (e.g. what are the chances that the no.6 bus will arrive first) you can elicit the viewers subjective probability distribution @Hullman2016
- The big data paradox shrinks confidence intervals but magnifies bias [@Bradley2021] because the confidence intervals shrink due to the sample size but the imprecise target group creates bias.
- coloured maps for earthquake risk are easily interpretable @Spiegelhalter2017
- Hurricane risk is not only the path, but also the storm surge and wind speed. @Spiegelhalter2017

@@

# Previous literature review

##### Bivariate map
Depicts a bivariate map which uses a bivariate colour palette that is created by blending two single hue colour palettes. One colour represents the variable of interest while the other represents the sampling error of that variable. There are two immediate problems with this method. First of all, uncertainty is being expressed with hue and saturation which @Maceachren2012 found to be the worst aesthetics to map to uncertainty to as they don't have an intuitive interpretation. Value has a natural connection to uncertainty (lighter values equate to higher uncertainty and darker values equate to more certainty) so it is a much more appropriate choice. While the `Vizumap` data does depict areas of light and darkness, they are largely irrelevant to the uncertainty measure causing our heuristics to lead us to the incorrect conclusions. The Value-Suppressing Uncertainty Palettes (VSUP) shown in @fig-vsup maps estimates to the hue and error to the value thereby creating a more intuitive plot [@Correll2018]. Additionally, at high levels of uncertainty VSUP only has one output colour, which prevents viewers from decrypting any particular value and also avoids enforcing a binary encoding of significance [@Correll2018]. Unfortunately VSUP are not easy to combine with packages like `Vizumap` which leaves it still somewhat difficult to express this encoding in practice, however the combination of a bivariate map with VSUP has shown to improve decisions in the face of uncertainty [@Correll2018].

>>>>

- make sure quantified vs discussed uncertainty is mentioned
- industrial accidents have a "tollerable" risk chart based on risk and number of fatalities @Spiegelhalter2017
- @Suh2023 found that the main issue with deployment of AI was communication between data science and subject matter experts, since subject matter experts didn't want technical presentations that didn't explain exactly when and how a model would fail.
- People believe in the law of small numbers but dont believe in the lar of large numbers @Hullman2016
- experiencing an event makes your percieved probability higher than if you see a description of it @Hullman2016
- Frequency thing means that more effective communication to participants in a study means more effective science and we have a roll on effect @Hullman2016
- Probability judgements are less relative than other psychophysical judgements, 0%, 50% and 100% all have well understood meanings. Subjective probability distributions are spontaneous, and subjects are constructing a distribution upon being asked rather than articulating a fully formed mental representation of their beliefs. Therefore it is subject to heuristics. consider anchoring a scale with farmiliar probabilities . not sure if being asked for the entire distribution helps, e.g. the graphical one reduces noise but asking people for an interval estimation leads to overprecision and overconfidence @Hullman2016
- believed that offering enough decisions with varying rewards you can observe the true subjective probability, however whether or not probability is the right representation of subjective uncertainty is a topic of debate @Hullman2016
- she also discusses graphical interface (users have to draw the probability distribution) and framing probabilities as natural frequencies are better choices because they reduce noise and stuff.@Hullman2016
- Consider incorperating utility functions. Include "probability-coherence" checks @Hullman2016
- evidence that people do not follow the axioms of probability when conveying subjective probabilities. How do you deal with this as an analyst (e.g. if the probabilities do not sum to 1 @Hullman2016
- we consider a summary table as a visualisation, illuminate graphics with words and numbers, design graphics to allow a part-to-whole comparison on an appropriate scale, use images and metaphors to gain/retain attention but dont arouse undue emotion, assume low numeracy of a general public audience and adopt a less-is-more approach by reducing the need for inference and making clear and explicit comparison, be cautious about interactivity and animations (may introduce unnecessary complexity), avoid chart junk (like 3d bar charts) @Spiegelhalter2017
- @Maceachren2012 found to be the worst aesthetics to map to uncertainty to as they don't have an intuitive interpretation.

@@

- mentions uncertainty can be variance, precision, accuracy, reliability, or related concepts @Hullman2016
-  @Spiegelhalter2017 defines risk as risk known probabilities and uncertainty as estimated probabilities, therefore uncertainty is what we have when you cannot accurately quantify risk.
- Authors provide little justification for their chosen response models (e.g. absolute accuracy vs relative measures) @Hullman2016 
- Some questions (e.g. what are the chances that the no.6 bus will arrive first) you can elicit the viewers subjective probability distribution @Hullman2016
- The big data paradox shrinks confidence intervals but magnifies bias [@Bradley2021] because the confidence intervals shrink due to the sample size but the imprecise target group creates bias.
- coloured maps for earthquake risk are easily interpretable @Spiegelhalter2017
- Hurricane risk is not only the path, but also the storm surge and wind speed. @Spiegelhalter2017

@@

# Previous literature review
##### Introduction addition
From entertainment choices to news articles to insurance plans, the modern citizen is so over run with information in every aspect of their life it can be overwhelming. So overwhelming in fact, that it is not uncommon for people to become so overwhelmed by the information they refuse to engage with it at all. In this overflow of information, tools that can effectively summarise information down into simple and clear ideas become more valuable. While websites that summarise insurance plans or hotel options down into a clear table make a living off it, few tools are as powerful or effective as a visualisation. Information visualisations remain one of the most powerful tools for fast and reliable science communication. Effectively leveraging visualisations to make them more effective is therefore key in facilitating simple and clear communication of science and other ideas.
